Graphical Tests for Power Comparison of Competing Designs

### 2012-03-27 experiment.tex
experimental setup

>>>>

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3in]{turk4_samplesize_correctn.pdf}  
   \caption{For each sample size for polar and Euclidian coordinates, the bars are colored according to the number of correct responses. Darker colors indicate lower accuracy levels while lighter colors indicate higher accuracy levels. }
   \label{samp_size_acc}
\end{figure}

The difficulty of the charts is largely determined by the sample size taken from the original data set. Samples of 24 \% generally result in higher accuracy as the extra information facilitates detection of a relationship. Figure \ref{accuracy_preds} shows the relationship between the number of correct responses relative to the total number of responses and how this relationship differs between Euclidian and polar coordinates. The bars in the Euclidian plot are overall a lighter color than they are in the polar plot. This indicates a higher level of accuracy at all sample sizes. For Euclidian coordinates, we can see a stair step pattern in the accuracy levels as sample size increases. Lower levels of accuracy, indicated by darker colors, become consistently less prevelant as sample size increases. The relationship between sample size and accuracy level is not as simple for polar coordinates. Sample sizes of 2\% and 4\% have very similar accuracy levels. After 6\% the stair step pattern becomes visible and similar to that of Euclidian coordinates. Sample size seems to have less of an effect on accuracy for polar coordinates than it does for Euclidian coordinates.

### 2012-03-27 setup.tex
experimental setup

\subsection{Wind Direction and Airport Efficiency}
Deciding on the design: since wind direction is circular, we used (conditional) wind rose charts - i.e. for each of 36 wind directions we show the percentage of flights falling into specific time intervals between successive flights: 0, 1, ..., 7, and 8+ minutes.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
   \begin{tabular}{ccl}
   \includegraphics[width=0.375\linewidth]{Euclidian_NoLine.pdf} & \hspace{-.3in}
   \includegraphics[width=0.375\linewidth]{Euclidian_Line.pdf} &  \hspace{-.25in} \multirow{2}{*}[.55in]{  \includegraphics[width=0.2\linewidth]{legend.pdf}} \\
   \includegraphics[width=0.43\linewidth]{Polar_NoLine.pdf} &  \hspace{-.3in}
   \includegraphics[width=0.43\linewidth]{Polar_Line.pdf}  
   \end{tabular}
   \caption{All four competing designs: polar versus Euclidean charts in top and bottom row, with (right) and without (left) reference lines at 50\%. }
   \label{layouts}
\end{figure}

In spite of the contextual circular property of wind direction, the pattern in efficiency did not seem to stand out much during the exploration process, which led us to using a corresponding  Euclidean design. Both designs were additionally equipped with a reference line at 50\%.

Figure \ref{layouts} shows an overview of all four chart types in the study.

>>>>

\subsection{Wind Direction and Airport Efficiency}
In deciding on the design for displaying efficiency  by wind direction we were using the fact that wind direction is circular, and  displayed the data as (conditional) wind rose charts - i.e. for each of 36 wind directions we show the percentage of flights falling into one-minute intervals between successive flights, from  0 minutes to 8 minutes or more.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
   \begin{tabular}{ccl}
   \includegraphics[width=0.375\linewidth]{Euclidian_NoLine.pdf} & \hspace{-.3in}
   \includegraphics[width=0.375\linewidth]{Euclidian_Line.pdf} &  \hspace{-.25in} \multirow{2}{*}[.55in]{  \includegraphics[width=0.2\linewidth]{legend.pdf}} \\
   \includegraphics[width=0.43\linewidth]{Polar_NoLine.pdf} &  \hspace{-.3in}
   \includegraphics[width=0.43\linewidth]{Polar_Line.pdf}  
   \end{tabular}
   \caption{All four competing designs: polar versus Euclidean charts in top and bottom row, with (right) and without (left) reference lines at 50\%. }
   \label{layouts}
\end{figure}

In spite of the contextual circular property of wind direction, the pattern in efficiency did not seem to stand out well during the exploration process, which led us to using a corresponding  Euclidean design. Both designs were additionally equipped with a reference line at 50\%. 
Figure \ref{layouts} shows an overview of all four chart types in the study.
